### 2020-03-20 thesis/content/chapter-graph-lta.tex
started with description of gcnn lta relation

Now we will look at the \ac{gcnn} approaches described in \cref{sec:related:gcr:nn} from an \ac{lta} perspective.
While the \ac{svm} \ac{lta} formulation from \cref{thm:ltag:svm-ltag-formulation} uses a single fixed aggregation function, namely $\wmaj$, \ac{gcnn} architectures can use many other aggregation functions.
As illustrated in x, this is due to the fact that the structure of \acp{gcnn} aligns more closely to that of \ac{lta}:
The decomposition and local evaluation functions are implicitly defined by the convolutional layers, the aggregation function directly corresponds to the pooling layer in existing architectures.

>>>>

Now we will look at the \ac{gcnn} approaches described in \cref{sec:related:gcr:nn} from an \ac{lta} perspective.
As described in the last section, \acp{svm} can be interpreted as \ac{lta} methods if they use an \ac{sce} embedding;
similarly \acp{gcnn} also have \ac{lta} formulations under certain conditions that are described in this section.

While the \ac{svm} \ac{lta} formulation from \cref{thm:ltag:svm-ltag-formulation} uses a single fixed aggregation function, namely $\wmaj$, the aggregation function in \ac{gcnn} architectures can be chosen more freely.
This is due to the fact that \acp{gcnn} have an \ac{lta} formulation in which the convolutional layers implicitly define the decomposition and local evaluation functions while the pooling layer directly corresponds to the \ac{lta} aggregation function.
This correspondence is illustrated in \cref{fig:ltag:gcnn-structure}.
\begin{figure}[t]
	\centering
	\includegraphics[width=0.8\linewidth]{gfx/graph-lta/gcnn-structure.pdf}
	\caption{
		An \ac{lta} perspective on \acp{gcnn} that use vertex neighborhood convolutions.
	}\label{fig:ltag:gcnn-structure}
\end{figure}
As described in \cref{sec:related:gcr:nn}, a stack of $T$ vertex convolution layers computes a feature vector $z_i \in \mathbb{R}^{(T)}$ for all vertices $v_i \in \mathcal{V}_G$ of an input graph $G$.
Depending on the specific type of convolutional layer, each of those feature vectors $z_i$ is the result of some subset of the input feature vectors ${\{ x_i \}}_{v_i \in \mathcal{V}_G}$:
\begin{enumerate}[label=\textbf{\arabic*.}]
	\item \textbf{Spectral convolutions with arbitrary filters:}
	\item \textbf{Spatial vertex convolutions:}
		If the convolutional layers use a neighborhood aggregation scheme, the receptive field of vertices that have an influence on $z_i$ is equal to the 1-\acs{wl} subtree of $v_i$ after $T$ refinement steps as described by \citet{Xu2018}.
		Similar to the \ac{wl} subtree kernel, each $z_i \in \mathbb{R}^{(T)}$ can therefore be interpreted as the evaluation of a localized subtree.
\end{enumerate}
